\documentclass[11pt]{article}
\usepackage[total={6.7in,9.4in}]{geometry}
\usepackage{hyperref}
\usepackage{framed}
\usepackage{wasysym}
\usepackage{marvosym}
\usepackage{ifsym}
\usepackage[usenames, dvipsnames]{color}
\definecolor{mygray}{gray}{0.9}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
}

\def\Vhrulefill{\leavevmode\leaders\hrule height 1.2ex depth \dimexpr2pt-0.5ex\hfill\kern0pt}
\def\VhrulefillThin{\leavevmode\leaders\hrule height 0.7ex depth \dimexpr1pt-0.7ex\hfill\kern0pt}
\date{}
\pagenumbering{gobble}

\begin{document}
\noindent{\textbf{Neeraj Kumar} \hfill \phone : +1-805-886-2271} \\
\noindent{\href{http://sud03r.github.com}{sud03r.github.com} \hfill \Letter : \href{mailto:neeraj@cs.ucsb.edu}{neeraj@cs.ucsb.edu}

\noindent\VhrulefillThin \\

\noindent Computer enthusiast with over eight years of experience in computer science research and engineering.\\

\noindent\textsc{Education}
\textcolor{mygray}{\noindent\Vhrulefill}
\begin{itemize}
	\item \textbf{University of California, Santa Barbara} \hfill(Fall 2015 - Winter 2020)\\
		Ph.D Computer Science~ (Graph and Geometric Algorithms)\\
    Thesis title: \emph{Geometric Constraint Removal and Related Problems}
	
	\item \textbf{University of Waterloo, Canada} \hfill(Fall 2013 - 2015) \\
		Master of Mathematics, Computer Science (Algorithms and Complexity)\\
		Thesis title: \emph{Width properties of control-flow graphs and applications}

	\item \textbf{Indian Institute of Technology, Varanasi, India} \hfill(2006 - 2010)\\
		Bachelors in Computer Science
\end{itemize}
\medskip

\medskip
\noindent\textsc{Work Experience}
\textcolor{mygray}{\noindent\Vhrulefill}
\begin{itemize}

	\item \textbf{PhD Intern, Facebook Inc.}, Cambridge, MA \hfill(June 2019 - Sept 2019) \\
				Algorithms for Data Warehouse Graph Compression

	\item \textbf{Graduate Technical Intern, Intel Corporation}, Hillsboro, OR \hfill(June 2018 - Sept 2018) \\
        Algorithms for Computing Visibility between Polygon Edges.
	
	\item \textbf{Graduate Technical Intern, Intel Corporation}, Santa Clara, CA \hfill(June 2016 - Sept 2016) \\
        Geometric Algoritms for Layout Processing.
	
	\item \textbf{Senior Member of Technical Staff, Mentor Graphics}, India \hfill(May 2010 - Aug 2013) \\
				Algorithmic solutions for Mentor's next generation emulation platform.
	
\end{itemize}

\noindent\textsc{Technical Skills}
\textcolor{mygray}{\noindent\Vhrulefill}
\begin{itemize}
	\item \textbf{Programming languages} C++(Proficient), C, Perl, Python, php, bash (Good), Java (basic)
	\item \textbf{Operating systems/Tools} Linux (Ubuntu), GDB, version control (git, svn, cvs), awk, sed
	\item \textbf{Other} Graph Algorithms (Proficient), Computational Geometry (Proficient)
\end{itemize}

\noindent\textsc{Publications\footnote{Unless marked with $*$, authors are listed in alphabetical order}}
\textcolor{mygray}{\noindent\Vhrulefill}
\begin{enumerate}
		
		\item \textbf{Approximating Min-Color Path on Color-Connected Planar Graphs}
				
				\emph{Neeraj Kumar}, Daniel Lokshtanov, Saket Saurabh and Subhash Suri
				\textbf{(In Submission, 2020)}

		\item \textbf{The Maximum Exposure Problem}
				
				\emph{Neeraj Kumar}, Stavros Sintos and Subhash Suri \emph{at}
				\textsc{Approx 2019, MIT, USA}

		\item \textbf{Computing a Minimum Color Path in Edge-Colored Graphs}
				
				\emph{Neeraj Kumar} \emph{at} Symposium of Experimental Algorithms \textsc{(SEA) 2019, Kalamata, Greece}

    \item \textbf{Improved Approximation Bounds for the Minimum Constraint Removal Problem}
				
				S. Bandyapadhyaya,  \emph{N. Kumar}, S. Suri and K. Varadrajan \emph{at} 
				\textsc{Approx 2018, Princeton, USA} \\ 
				Journal version appeared in \emph{Computational Geometry: Theory and Applications, 2020}

    \item \textbf{Computing Shortest Paths in the Plane with Removable Obstacles}
        
				Pankaj K Agarwal, \emph{Neeraj Kumar}, Stavros Sintos and Subhash Suri \emph{at} \\
				Scandinavian Symposium and Workshops on Algorithm Theory (SWAT) 2018, Malmo, Sweden.
    
    \item \textbf{Shortest paths in the plane with Violations.}
        
				John Hershberger, \emph{Neeraj Kumar} and Subhash Suri \emph{at} \\
        European Symposium of Algorithm (ESA) 2017, Vienna, Austria\\
				Journal version appeared in \textbf{Algorithmica, 2020}

    \item \textbf{Counting Convex $k$-gons in an Arrangement of Line Segments} 
        
				Martin Fink, \emph{Neeraj Kumar} and Subhash Suri \emph{at} \\
        Canadian Conference on Computational Geometry (CCCG), 2016 Vancouver, Canada.

    \item \textbf{SiPTA: Signal Processing for Trace-based Anomaly Detection$^*$}
        
				\emph{Authors:} MM Zeinali, MA Salem, \textbf{N Kumar}, G Cutulenco and S Fischmeister, \emph{at}\\
				International Conference on Embedded Software \textsc{(Emsoft)} 2014
\end{enumerate}

\medskip
\noindent\textsc{Other projects}
\textcolor{mygray}{\noindent\Vhrulefill}
\begin{itemize}
	\item \emph{Computational Geometry Challenge 2020} : Algorithms for minimum convex partition problem.
	\item \emph{Google Summer of Code 2014} (OGDF) : Algorithms for treewidth of undirected graphs.
	\item \emph{Google Summer of Code 2010} (ScummVM) : Game engine for testing ScummVM subsystems.
	\item Implemented neural network based model for traffic sign detection.
	\item Performed a holistic analysis of shared library performance on NUMA machines.
\\
\end{itemize}

\noindent\textsc{Select Graduate Coursework}
\textcolor{mygray}{\noindent\Vhrulefill}
\medskip
\begin{itemize}
    \item[$-$] Computational Geometry ~\hspace{8em} $-$ Graph-theoretic Algorithms
    \item[$-$] Foundations of Data Science ~\hspace{7em} $-$ Advanced Data Mining and Machine Learning
\end{itemize}

\noindent\textsc{Miscellaneous}
\textcolor{mygray}{\noindent\Vhrulefill}
\begin{itemize}
	\item \textbf{Scholarships and Awards} 
        \begin{itemize}
            \item[$-$] Distinguished Graduate Student Speaker (UCSB), 2018.
            \item[$-$] Lead Teaching Assistant, Computer Science (UCSB), 2017-18.
            \item[$-$] Outstanding Teaching Assistant (UCSB), 2015-16.
            \item[$-$] Graduate Entrance Scholarship (UWaterloo), 2013.
        \end{itemize}

	\item \textbf{Teaching assistant}~~ 
			
        \begin{itemize}
					\item[$-$] \emph{Graduate courses:} CS 235 (Computational Geometry), CS 231 (Advanced Algorithms)
					\item[$-$] \emph{Undergraduate courses:} CS 130A, 130B (Algorithms and Data Structures, UCSB) CS341 (Algorithms, UWaterloo) 
        \end{itemize}

	\item \textbf{Languages}~~ English (fluent), Hindi(fluent)
\end{itemize}

\end{document}
